Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-12 ms.tex
mention emission predictions section at end of intro, other minor clean-up

% might be more appropriate to cite the 2D dust map Eddie is making rather
% than the `methods' paper

In $\S$\ref{sec:data} we introduce the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the \PLANCK~maps to 
isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
explain the dust emission model we apply to the \PLANCK~and \IRAS/DIRBE data. 
In $\S$\ref{sec:bpcorr}, we discuss the details of predicting 
\PLANCK~observations based on this dust model. In $\S$\ref{sec:global} we 
derive constraints on our model's global parameters based on the \PLANCK~High 
Frequency Instrument (HFI) maps. In $\S$\ref{sec:fitting} we detail the Markov 
chain Monte Carlo (MCMC) method with which we have estimated the spatially 
varying parameters of our model. In $\S$\ref{sec:ebv} we calibrate our derived 
optical depth to reddening at optical wavelengths. In $\S$\ref{sec:release} we 
present the full-sky maps of dust temperature and optical depth we have 
obtained, and conclude in $\S$\ref{sec:conclusion}.

@@

% in previous sentence, think it might be better to only quote rms, and
% omit the ranges of values for each parameter ?

@@

\section{Low-frequency Emission Predictions}
FDS99 originally performed their \PLANCK+DIRBE dust SED analysis for the sake 
of accurately forecasting low-frequency CMB foregrounds. Recently, Galactic CMB
foregrounds, especially in the 100-150 GHz frequency range, have become a focal
point of cosmology owing to the \cite{bicep2} $B$-mode polarization results. 
Here we show that our two-component foreground predictions are more accurate 
than those based on the \cite{planckdust} single-MBB model over the 100-217 GHz
frequency range.

>>>>

In $\S$\ref{sec:data} we introduce the data used throughout this study. In 
$\S$\ref{sec:prepro} we describe our preprocessing of the \PLANCK~maps to 
isolate thermal emission from Galactic dust. In $\S$\ref{sec:modeling} we 
explain the dust emission model we apply to the \PLANCK~and \IRAS/DIRBE data. 
In $\S$\ref{sec:bpcorr}, we discuss the details of predicting 
\PLANCK~observations based on this dust model. In $\S$\ref{sec:global} we 
derive constraints on our model's global parameters based on the \PLANCK~High 
Frequency Instrument (HFI) maps. In $\S$\ref{sec:fitting} we detail the Markov 
chain Monte Carlo (MCMC) method with which we have estimated the spatially 
varying parameters of our model. In $\S$\ref{sec:ebv} we calibrate our derived 
optical depth to reddening at optical wavelengths. In $\S$\ref{sec:lofreq} we
evaluate the accuracy of our two-component thermal dust emission predictions 
from 100-217 GHz. In $\S$\ref{sec:release} we present the full-sky maps of dust
temperature and optical depth we have obtained, and conclude in 
$\S$\ref{sec:conclusion}.

@@

@@

\section{Low-frequency Emission Predictions}
\label{sec:lofreq}
FDS99 originally performed their \PLANCK+DIRBE dust SED analysis for the sake 
of accurately forecasting low-frequency CMB foregrounds. Recently, Galactic CMB
foregrounds, especially in the 100-150 GHz frequency range, have become a focal
point of cosmology owing to the \cite{bicep2} $B$-mode polarization results. 
Here we show that our two-component foreground predictions are more accurate 
than those based on the \cite{planckdust} single-MBB model over the 100-217 GHz
frequency range.
